Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-17 paper/main.tex
Statistical analysis, please check

% similar to previous studies
On the first level, we created GLM contrasts based on annotated stimulus
features embedded in the in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of non-spatial information
differently in five $t$-contrasts for the movie stimulus (Tab.~\ref{tab:av-contrasts})
and eight $t$-contrasts for the audio-description stimulus (Tab.~\ref{tab:ao-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA but chose one contrast to be the ``primary contrast'' for
later detailed inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well the average of events within
categories represented spatial information and non-spatial information
respectively (cf. section \ref{rationale}), and b) the amount of available data.
% AV: primary contrast
In the primary contrast of the movie stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vse\_new}) to cuts merely switching the camera
position within a setting that was already established earlier in the movie
(\texttt{vpe\_old}).
% why
We assumed that the category \texttt{vse\_new} on average comprised the most
movie frames depicting a landscape or the geometry of a setting, and the
category \texttt{vpe\_old} the most frames depicting persons, faces, or objects
[(cf.  rationale to categorize the cuts in section \ref{rationale})].
% AD: primary contrast
In the primary contrast of the audio-description stimulus, we contrasted buildings and
landmarks (\texttt{geo}), and rooms and geometry-defining objects
(\texttt{groom}) with not just nouns referring to a person's head or face
(\texttt{fahead}, N=83; e.g.  ``eyes'', ``face'', or ``head'') but also all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture} to get more events per stimulus segment.\todo{ouff}
% why furniture was not used
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived as either a
geometry-defining scene element or as an isolated object.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the
first time (\texttt{se\_new}) or a setting that recurred during the plot
(\texttt{se\_old}) were not included in the primary contrast because
% heterogeneous category
a) categories comprise nouns that could count as a member of another category
(e.g. ``[a] physician''; section \ref{rationale}), and
% richness of verbal description vs. picture
b) nouns that only vaguely describe a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures].
% and c) the narrator is often lacking behind a short dialogue or a change of
% the soundscape that might already indicate a change of settings.

% control contrasts
Finally, we created several $t$-contrasts as negative controls for both stimuli
(Tab.~\ref{tab:av-contrasts} and Tab.~\ref{tab:ao-contrasts}).
% AV: no cut > cut
For the movie stimulus, four contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by contrasting
nouns spoken by the narrator.
% AD stimulus
For the audio-description stimulus, we created five $t$-contrasts
(Tab.~\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts.

% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
% (2010)
In the block-design localizer study using the established approach of contrasting blocks of
pictures, a set of three contrasts (\textit{strict}, \textit{relaxed}, and
\textit{simple} was created contrast (cf. \citep{sengupta2016extension}).

@@

% alignments single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
participant and segment was performed in functional space preserving the orientation
of the EPI images.
% two ways of co-registration
Participant-specific BOLD T2* time series were anatomically co-registered in two
ways:
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
a) via linear transformation to a participant-specific, study-specific T2* template
(cf. \citep{sengupta2016extension}), and
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
b) via non-linear transformation to a study-specific T2* group template (cf.
\citep{hanke2014audiomovie}).
% MNI152
This group template was co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures.

% second level model
The second level analyses which averaged contrast estimates over the eight
stimulus segments were carried out using a fixed effects model by forcing the
random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed
Effects; \citep{beckmann2003general, woolrich2004multilevel}.
% thresholding ($Z$>2.3 in subject-space; $Z$>3.4 in group space)
(Gaussianised T/F) statistic images were thresholded using clusters determined
by $Z$>3.4 and a cluster-corrected significance threshold of $p$<.05
\citep{worsley2001statistical}.

% third level model
The third level analysis which averaged contrast estimates over participants was
carried out using FLAME stage 1 with automatic outlier detection
\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
% thresholding
Here again, Z (Gaussianised T/F) statistic images were thresholded using
clusters determined by $Z$>3.4 and a (corrected) cluster significance threshold of
$p$<.05 \citep{worsley2001statistical}.
% brain region identification
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
% PPA masks
Regions of interest (ROI) masks for individual PPAs and a PPA group mask of
individual PPA overlaps were created from data provided by
\citep{sengupta2016extension}.

>>>>

Given the rich naturalistic stimuli and the availability of various stimulus
feature annotations, there are several candidates for implementing contrasts to
identify hemodynamic activity congruent with the hypothesized processing of
spatial information in the PPA. However, while the rationale for any contrast
composition must be sound, the selection of a single implementation remains
arbitrary to some degree. Consequently, we computed multiple contrasts that are
listed in Tables~\ref{tab:av-contrasts} and \ref{tab:ao-contrasts} for movie
and audio-description, respectively. For each stimulus we, subjectively, picked
a primary contrast for result presentation (the first one in each Table) based
on how well the average event within categories represents spatial and
non-spatial information, and the number of events in the stimulus.
An evaluation of the robustness of these results with respect to similar but
different contrasts is available in the supplementary materials.

% AV: primary contrast
In the primary contrast for the movie stimulus, we contrasted cuts to a setting
that was not depicted before (\texttt{vse\_new}) to cuts merely switching the
camera position within a setting that was already established earlier in the
movie (\texttt{vpe\_old}), because the former are designed to orient the viewer
in the movie environment using wider-camera angles, whereas the latter can
afford to depict details of a scene.
% AD: primary contrast
In the primary contrast of the audio-description stimulus, we contrasted
mentions of buildings and landmarks (\texttt{geo}), and rooms and
geometry-defining objects (\texttt{groom}) with noun occurence referring to a
person's head or face (\texttt{fahead}), and other non-geometry related
categories (\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
\texttt{sex\_f}, \texttt{sex\_m}).

% why furniture was not used
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived as either a
geometry-defining scene element or as an isolated object.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the
first time (\texttt{se\_new}) or a setting that recurred during the plot
(\texttt{se\_old}) were not included in the primary contrast because
% heterogeneous category
a) they comprise nouns that could be a member of another category (e.g. ``[a]
physician''), and
% richness of verbal description vs. picture
b) nouns that only vaguely identify a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') compared to perceptually richer
descriptions.

% control contrasts
Finally, we created several control contrasts for both stimuli
(Tab.~\ref{tab:av-contrasts} and Tab.~\ref{tab:ao-contrasts}).
% AV: no cut > cut
For the movie stimulus, four contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by contrasting
nouns spoken by the narrator.
% AD stimulus
For the audio-description stimulus, we created five control contrasts
(Tab.~\ref{tab:ao-contrasts}) to test if activation in the PPA was
correlated with moments of cuts, despite the absence of visual stimulation.

@@

% alignments single subjects (for Bland-Altman-Plots) 1st level
First-level GLM analyses were performed in the image-space of a participant-specific BOLD
T2* template
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
using a previously determined linear transformation \citep{sengupta2016extension}.
For higher-level analyses image data were aligned with a study-specific T2* group template
likewise using a previously computed non-linear transformation \citep{hanke2014audiomovie}.
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
% MNI152
This group template was co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom).

% second level model
The second level analyses, which averaged contrast estimates over the eight
stimulus segments, were carried out using a fixed effects model by forcing the
random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed
Effects; \citep{beckmann2003general, woolrich2004multilevel}.
% thresholding ($Z$>2.3 in subject-space; $Z$>3.4 in group space)
(Gaussianised T/F) statistic images were thresholded using clusters determined
by $Z$>3.4 and a cluster-corrected significance threshold of $p$=.05
\citep{worsley2001statistical}.

% third level model
The third level analysis which averaged contrast estimates over participants was
carried out using FLAME stage 1 with automatic outlier detection
\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
% thresholding
Here again, Z (Gaussianised T/F) statistic images were thresholded using
clusters determined by $Z$>3.4 and a corrected cluster significance threshold of
$p$=.05 \citep{worsley2001statistical}.
% brain region identification
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
% PPA masks
Regions of interest (ROI) masks for individual PPAs and a PPA group mask of
individual PPA overlaps were created from data provided by
\citep{sengupta2016extension}.
